A Detection of the Environmental Dependence of the Stellar Halos of Massive Central Galaxies

### 2017-03-14 draft/ms_v6.tex
New draft

% Packages
\usepackage{deluxetable}
%\usepackage{apjfonts}
\usepackage{newtxtext,newtxmath}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{amssymb, amsmath}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{float}
\usepackage[usenames, dvipsnames]{color}

@@

\def\etal{{\ et al.~}}
\def\galfit{{\tt GALFIT}}
\def\ser{{S\'{e}rsic\ }}
\def\redm{\texttt{redMaPPer}}
\def\cmodel{\texttt{cModel}}
% Samples
\def\rbcg{\texttt{cenHighMh}}
\def\nbcg{\texttt{cenLowMh}}
\def\redbcg{{$\lambda \ge 30$}}
\def\nonbcg{{$\lambda < 20$}}
% Mass related 
\def\mstar{{$M_{\star}$}}
\def\mhalo{{$M_{\mathrm{halo}}$}}
\def\logms{{$\log (M_{\star}/M_{\odot})$}}
\def\logmh{{$\log (M_{\mathrm{Halo}}/M_{\odot})$}}

@@

\author[S. Huang et al.]{Song Huang,$^{1,2}$\thanks{E-mail: song.huang@ipmu.jp (SH)}
        HSC collaboration$^{3}$   
        \\ \\
        % List of institutions
        $^{1}$Kavli-IPMU, The University of Tokyo Institutes for Advanced Study, 
              the University of Tokyo (Kavli IPMU, WPI), Kashiwa 277--8583, Japan\\
        $^{2}$Department of Astronomy and Astrophysics, University of California 
              Santa Cruz, 1156 High St., Santa Cruz, CA 95064, U.S.A\\
        $^{3}$Another Department, Different Institution, Street Address, City Postal 
              Code, Country
        }

@@

    The promising hierarchical assembly scenario of massive galaxies suggest the 
    structure of these galaxies should depend on their environments or halo mass.
    Yet, at low redshift, observations find no clear evidence for that. 
    Here, using the deep images from the Subaru Hyper Suprime-Cam (HSC) survey,
    we map the stellar mass distributions of massive galaxies at $0.3 < z < 0.5$ 
    out to the very outskirt, and detect subtle, but robust structural differences 
    that depend on halo mass for central galaxies at high mass end. 
    With the help of the \redm{} catalog, we separate these massive galaxies 
    into centrals of halos that are more and less massive than 
    $M_{200m}\sim 10^{14} M_{\odot}$.
    For centrals with similar stellar mass within 100 kpc, the ones from 
    more massive halos on average have slightly more flattened inner profile 
    within $\sim 10$-$20$ kpc, and more prominent outer envelope.
    Meanwhile, when matched at the same stellar mass within inner 10 kpc--a 
    proxy of the mass of the in-situ component, the massive centrals of more  
    massive halos show much more significant outer stellar envelopes.    
    We also see that these two samples of massive galaxies follow slightly 
    different mass-size relation and the relationship between the stellar mass 
    within 100 and 10 kpc.
    Such differences in structure are broadly consistent with the expectation that
    central galaxy from more massive halo should have more complex merging history.
    These results highlight the importance of deep photometry in the study of 
    the assembly history of massive galaxies.

@@

%% ------------------------------------------------------------------------------------ %% 
    \begin{figure*}
        \centering 
        \includegraphics[width=\textwidth]{fig/redbcg_sdss_compare}
        \caption{
            A comparison between the imaging quality of SDSS and HSC Wide for a sample 
        	of nearby massive elliptical galaxies at $0.2 < z < 0.5$.  
            These images are generated using $gri$ band images with an arcsinh stretch 
            \citep{Lupton2004}. 
            The HSC \texttt{WIDE} layer is $3.0$-$4.0$ magnitudes deeper than SDSS 
            which is critical to map the outskirts of ETGs out to large radii.
            }
        \label{fig:sdss_compare}
    \end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_m100_m10_compare}
      \caption{
          Three-color images for a subsample of massive galaxies at $z\sim 0.4$, and 
          with similar values for their \mstar{} within a 10 kpc aperture 
          (the dash-line circle on top-left figure indicates the scale of 10 kpc;
          $11.2<\log (M_{\star,10\ \mathrm{kpc}}/M_{\odot})<11.3$). 
          Galaxies are rank-ordered from top to bottom and from left to right by 
          their \mstar{} within 100 kpc aperture which varies from $10^{11.2} M_{\odot}$ 
          to $10^{11.7} M_{\odot}$. 
          At fixed "inner" mass ($M_{\star,10}$), massive galaxies display significant
          diversity in their outer profiles. 
          Red boxes indicate galaxies in halos more massive than 
          $\sim 10^{14.0} M_{\odot}$. 
          }
      \label{fig:m100_m10_color}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    Massive galaxies are unique laboratories to study both cosmology and galaxy 
    formation. 
    Although the hierarchical growth scenario under the $\Lambda$-CDM cosmology 
    is a solid theoretical background (e.g. \citealt{Baugh1996, DeLucia2006}, 
    plenty important questions regarding the star-formation history, mass assembly 
    process, and structural evolution of these massive galaxies remain open. 
    Thanks to the advances in observations and numerical simulations, the newly 
    developed ``two-phase'' formation scenario (e.g. \citealt{Oser2010, Oser2012}) 
    becomes the most promising theory that can reasonably explain different 
    observations of massive galaxies. 
    Under this picture, the highly dissipative processes at high-$z$ (e.g cold 
    accretion, gas-rich merger; e.g. \citealt{Hopkins2008, Dekel2009}) induce 
    intense starburst, and quickly form the massive progenitors of $z\sim 0$ massive 
    early-type galaxies (ETGs).     
    Later, certain physical mechanism (e.g. AGN feedback; e.g. \citealt{Sijacki2007,
    Fabian2012}) 
    efficiently quenched the on-going star formation so that a large fraction of 
    these massive progenitors become quiescent at $z>1$ (e.g. \citealt{Bezanson2009,
    Kriek2016}). 
    At the same stellar mass (\mstar{}), these so-called ``red nuggets'' 
    (e.g. \citealt{Damjanov2009}) have smaller effective radius 
    ($R_{\mathrm{e}}$; \citealt{Trujillo2006, vanDokkum2008, Cimatti2008}), 
    slightly higher central velocity dispersion and stellar mass density 
    (\mden{}; e.g. \citealt{vandeSande2011, Belli2014}), more disk-like morphology 
    (e.g. \citealt{vanderWel2011}) than their local descendants 
    (e.g. \citealt{Bezanson2009, vanDokkum2010}). 
    Later, the second phase of evolution is driven by non-dissipative processes 
    like dry mergers with other galaxies (e.g. \citealt{Naab2006, Khochfar2006}). 
    According to the ``two-phase'' scenario, minor mergers make dominated 
    contribution during this period as they help explain the significant increase
    of $R_{\mathrm{e}}$ (e.g. \citealt{Newman2012, vdWel2014}) and accumulation of 
    outer stellar halo (e.g.  \citealt{Szomoru2012, Patel2013}).

    Despite the great success, it also raises new questions. 
    Under the $\Lambda$-CDM cosmology, the formation of galaxy is intrinsically 
    tied to the growth of the host dark matter halo 
    (e.g. \citealt{Leauthaud2012, Behroozi2013}).
    Massive ETGs living in the center of more massive halos should experience 
    different mass assembly history and undergo different merging events comparing 
    to the ones from smaller halos. 
    Therefore, it is reasonable to expect that the structures of massive galaxies
    depend on the ``environment''\footnote{Although there are different 
    observational definition of environment, we use the term ``environment'' and 
    halo mass interchangeably in this work.}.

    As one of the most important structural parameters, the $R_{\mathrm{e}}$ of 
    massive ETGs follows a tight and steep relation with the \mstar{} 
    (e.g. \citealt{Shen2003, Guo2009}). 
    Models based on the ``two-phase'' formation scenario naturally predict that 
    such mass--size relation should show environmental dependence, and 
    $R_{\mathrm{e}}$ of massive ETGs in more massive halos should be larger 
    than the ones in less massive halos at fixed \mstar{} 
    (e.g. \citealt{Shankar2013, Shankar2014}). 
    Interestingly, while hints of such dependence have been spotted at high-$z$ 
    (e.g. \citealt{Papovich2012, Lani2013, Delaye2014}; but also see 
    \citealt{Rettura2010}), solid evidence of it at low-$z$ is still absence 
    (e.g. \citealt{Nair2010, HCompany13}; but also see \citealt{Yoon2017}).
    This confusing result becomes a challenge to the hierarchical growth model 
    of massive galaxies. 
    On the observational side, both the depth of the images and the photometric 
    method contribute to this problem. 
    The steep inner \mden{} profiles, extremely extended stellar envelopes, 
    and other structural details make it very difficult to accurately define and 
    measure the \mstar{} and $R_{\mathrm{e}}$ of massive ETGs 
    (e.g. \citealt{Bernardi2013, DSouza2014}).

    Here, taking advantage of the excellent image quality of the HSC survey, we 
    investigate the environmental dependence of structure in massive galaxies 
    via comparing the \mden{} profiles and structural scaling relations between 
    massive central galaxies living in more and less massive dark matter halos. 
    Both the deep imaging depth ($i$-band images are typically 3-4 magnitude deeper 
    than SDSS ones) and the good seeing condition (median FWHM$\sim 0.6^{\arcsec}$
    in $i$-band) of the HSC images make them perfect for mapping the \mstar{}
    distributions of massive galaxies out to very large radius (see 
    Fig~\ref{fig:sdss_compare}). 
    With the help of a cluster catalog, we select a large sample of massive central 
    galaxies in halos that are more or less massive than \logmh{}$\sim 14.0$ at 
    $0.3 < z < 0.5$ from the available $\sim 100$ square degree of HSC data.

    Motivated by the ``two-phase'' scenario, also due to the difficulty in 
    appropriately modeling the \mstar{} distributions of massive galaxies out to 
    their very outskirts, we focus on \mstar{} within two different physical apertures 
    in this work:

    \begin{itemize}
        \item \mstar{} within 10 kpc, \minn{}: according to the ``two-phase'' 
            scenario, the ``in-situ'' star-formation quickly built up the inner, dense 
            core of massive ETGs.  
            Based on recent observations and simulations (e.g.~\citealt{vanDokkum2010}; 
            \citealt{RodriguezGomez2016}), the in-situ 
            component distributes mostly within the effect radius ($R_{\mathrm{e}}$, 
            or 5-10 kpc) in massive galaxies.  
            Here we use \minn{} as a proxy of the \mstar{} formed in the ``in-situ''
            phase.  Although it is an empirical choice, the detailed comparison of 
            the stellar mass surface density (\mden{}) profiles later suggests it indeed 
            helps reveal interesting environmental dependence.  
            Under the adopted cosmology, $1.0^{\arcsec}$ in radius equals 4.4 and 6.1 kpc 
            at redshift 0.3 and 0.5.  
            We can reliably measure \minn{} without being bothered by smearing effect
            of seeing.
        \item \mstar{} within 100 kpc, \mtot{}: for massive galaxies in this work, 
            100 kpc aperture reaches to 5-10 $\times R_{\mathrm{e}}$ and very low 
            \mden{} region, hence can be treated as proxy of the ``total'' \mstar{}. 
            Limited by the accuracy of background subtraction, the \mden{} profile 
            of outer region can not be reliably recovered for massive galaxies across 
            our redshift range. 
            Although not perfect, \mtot{} is still a much better tracer of total 
            \mstar{} than the model-dependent ones using shallower images.
    \end{itemize}

    Massive central galaxies in this work show an intriguing diversity on the 
    plane defined by these two metrics.  
    We preview this using Fig~\ref{fig:m100_m10_color}, which shows a subsample of 
    massive galaxies at $z\sim 0.4$ that share very similar value of \minn{}, but show 
    a large range of outer structures. 
    Assuming galaxies at the same \minn{} have similar amount stars in the in-situ 
    component, it is of great interest to investigate the relation between their 
    environments and outer envelopes that are assembled at later time. 
    It is worth noting that, although a circular aperture is shown on 
    Fig~\ref{fig:m100_m10_color}, we always use elliptical apertures that follow the 
    average isophotal shape for photometry in this work.
    And, within our choices of redshift and \mstar{} ranges, we can safely ignore 
    significant mass growth and structural evolution 
    (no star formation, lower merger rate \etal~e.g.\ \citealt{Bellstedt2016},
    \citealt{Inagaki2015}; but also see \citealt{Bai2014}) 
    with our redshift and \mstar{} ranges.

    The paper is organized as follows. Section\ref{sec:data} gives a brief overview of 
    the HSC observation and data reduction, along with the summary of the data selection
    processes.  
    Then, we will explain the procedures for extracting 1-D surface brightness profiles 
    (Section \ref{sec:ellipse}) and estimating stellar mass (Section \ref{sec:mstar}) in
    details.   
    We will present the main results in Section \ref{sec:result}, and discuss the several 
    related technical and scientific issues in Section \ref{sec:discussion}, ending with
    summary and future plans in Section \ref{sec:summary}.

    All the magnitudes used here are in AB system (\citealt{Oke1983}), and are corrected 
    for Galactic extinction using calibrations from \citet{Schlafly11}.
    In this work, we assume $H_0$ = 70~km~s$^{-1}$ Mpc$^{-1}$, ${\Omega}_m=0.3$, 
    and ${\Omega}_{\lambda}=0.7$.

@@

    The Subaru Strategic Program (SSP, \citealt{MiyazakiInPrep}) makes use of the new 
    prime-focus camera, the Hyper Suprime-Cam (HSC;~\citealt{Miyazaki2012}), on the 
    8.2-m Subaru telescope at Mauna Kea. 
    The ambitious multi-layer HSC survey takes advantage of the large field of 
    view (FoV;~1.5 deg in diameter) of this camera and will cover $\sim 1400$ deg$^2$ 
    in 5 broad bands (\textit{g r i z Y}) to a limiting depth of $r \sim 26$ mag 
    in the \texttt{WIDE} layer. 
    This work is based on the internal data release \texttt{S15B}, which covers 
    $\sim 100$ deg$^2$ in all 5-band to full \texttt{WIDE} depth.  
    The regions covered by this release overlap with a number of spectroscopic surveys 
    (e.g.\ SDSS/BOSS: \citealt{Eisenstein2011}, \citealt{Alam2015}; 
    GAMA: \citealt{Driver2011}, \citealt{Liske2015}).

@@

    For each galaxy, \texttt{hscPipe} measures a \cmodel{} magnitude using an approach 
    that is similar to SDSS (\citealt{BoschInPrep}). 
    However, as opposed to SDSS, the HSC \cmodel{} is based on forced photometry which 
    means that it can accurately measure both the \textit{fluxes and colors of galaxies}. 
    The HSC \cmodel{} algorithm fits the flux distribution of each object using a 
    combination of a de~Vaucouleur and an exponential component and accounts for the PSF. 
    The performance of this algorithm has been tested using synthetic objects 
    (\citealt{SynPipeInPrep}), and the results indicate that, generally speaking, 
    the HSC \cmodel{} photometry is accurate down to $i >25.0$ mag.  
    However, \cmodel{} currently systematically underestimates the total fluxes of 
    massive ETGs with extended stellar distributions. 
    This is caused by an intrinsic limitation of \cmodel{} as it is incapable of
    modeling profiles with extremely extended outskirts, a problem that is exacerbated 
    at the depth of the HSC survey. 
    In addition, at the depth of the HSC survey, accurate deblending in the vicinity of
    large ETGs where satellites and background galaxies often blend with the low surface 
    brightness stellar envelope is a challenging problem. 
    The deblending method implemented by the \texttt{hscPipe} currently tends to 
    ``over-deblend'' the outskirts of bright galaxies and leads to un 
    under-estimation of the the total flux of massive ETGs (more discussion in 
    \citealt{BoschInPrep}).  
    For these reasons, our results will be based on custom developed code to measure 
    the luminosities and stellar masses of massive galaxies. 
    We use the HSC \texttt{hscPipe} photometry for two purposes: 
    1) to perform a first broad sample selection, and 2) to estimate the average 
    color of massive galaxies.

@@

    We begin by using a broad luminosity cut to select an initial sample of massive 
    galaxies at $z < 0.5$ from the HSC photometric catalog. 
    Based on Leauthaud\etal~(2016), galaxies with \logms{}$\geq 11.5$ mostly have 
    $i_{\mathrm{SDSS, cModel}} \leq 21.0$ mag. 
    We therefore select our initial sample to be brighter than 
    $i_{\mathrm{HSC, cModel}} \leq 21.5$\footnote{We neglect the insignificant 
    differences between the response curves of SDSS-$i$ and HSC-$i$ filters} 
    and also limit our sample to regions that have reached the required depth of 
    the \texttt{WIDE} survey in $i$-band.
    %% The SQL search is saved as "sample.sql" 
    %% The master catalog used here is "dr1_wide_galaxy_icmodel_21.5.fits"
    %%   The original catalogs contain 2275477 objects

>>>>

% Packages
\usepackage{deluxetable}
\usepackage{newtxtext,newtxmath}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{amssymb, amsmath}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{float}
\usepackage[usenames, dvipsnames]{color}

@@

\def\etal{{\ et al.~}}
\def\galfit{{\tt GALFIT}}
\def\ser{{S\'{e}rsic\ }}
\def\redm{\texttt{redMaPPer}}
\def\cmodel{\texttt{cModel}}
% Samples
\def\rbcg{\texttt{cenHighMh}}
\def\nbcg{\texttt{cenLowMh}}
\def\redbcg{{$\lambda \ge 30$}}
\def\nonbcg{{$\lambda < 20$}}
% Mass related 
\def\mstar{{$M_{\star}$}}
\def\mhalo{{$M_{\mathrm{halo}}$}}
\def\logms{{$\log (M_{\star}/M_{\odot})$}}
\def\logmh{{$\log (M_{\mathrm{halo}}/M_{\odot})$}}

@@

\author[S. Huang et al.]{
        Song Huang,$^{1,2}$\thanks{E-mail: song.huang@ipmu.jp (SH)}
        HSC collaboration$^{3}$   
        \\ \\
        % List of institutions
        $^{1}$Kavli-IPMU, The University of Tokyo Institutes for Advanced Study, 
              the University of Tokyo (Kavli IPMU, WPI), Kashiwa 277--8583, Japan\\
        $^{2}$Department of Astronomy and Astrophysics, University of California 
              Santa Cruz, 1156 High St., Santa Cruz, CA 95064, U.S.A\\
        $^{3}$Another Department, Different Institution, Street Address, City Postal 
              Code, Country
        }

@@

    The promising hierarchical assembly scenario of massive galaxies suggest the 
    structure of these galaxies should depend on their environments or halo mass.
    Yet, at low redshift, observations find no clear evidence for that. 
    Here, using the deep images from the Subaru Hyper Suprime-Cam (HSC) survey,
    we map the stellar mass distributions of massive galaxies at $0.3 < z < 0.5$ 
    out to the very outskirt, and detect subtle, but robust structural differences 
    that depend on halo mass for central galaxies at high mass end. 
    With the help of the \redm{} catalog, we separate these massive galaxies 
    into centrals of halos that are more and less massive than 
    $M_{\mathrm{Halo}}\sim 10^{14} M_{\odot}$.
    For centrals with similar stellar mass within 100 kpc, the ones from 
    more massive halos on average have slightly more flattened inner profile 
    within $\sim 10$-$20$ kpc, and more prominent outer envelope.
    Meanwhile, when matched at the same stellar mass within inner 10 kpc--a 
    proxy of the mass of the in-situ component, the massive centrals of more  
    massive halos show much more significant outer stellar envelopes.    
    We also see that these two samples of massive galaxies follow slightly 
    different mass-size relation and the relationship between the stellar mass 
    within 100 and 10 kpc.
    Such differences in structure are broadly consistent with the expectation that
    central galaxy from more massive halo should have more complex merging history.
    These results highlight the importance of deep photometry in the study of 
    the assembly history of massive galaxies.

@@

%% ------------------------------------------------------------------------------------ %% 
    \begin{figure*}
        \centering 
        \includegraphics[width=\textwidth]{fig/redbcg_sdss_compare}
        \caption{
            A comparison between the depth and imaging quality of SDSS and the HSC wide 
            layer for a sample of nearby massive elliptical galaxies at $0.2 < z < 0.5$.  
            These images are generated using $gri$ band images with an arcsinh stretch 
            \citep{Lupton2004}. 
            The HSC \texttt{WIDE} layer is $3.0$-$4.0$ magnitudes deeper than SDSS.
            This added depth is critical in order map the outskirts of ETGs out to 
            large radii.
            }
        \label{fig:sdss_compare}
    \end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_m100_m10_compare}
      \caption{
          Three-color images for a subsample of massive galaxies at $z\sim 0.4$. 
          All of these galaxies have the same mass within a 10 kpc aperture 
          ($11.2<\log (M_{\star,10\ \mathrm{kpc}}/M_{\odot})<11.3$). 
          The dash-line circle at the top-left figure indicates 10 kpc.
          Galaxies are rank-ordered from top to bottom and from left to right by 
          their \mstar{} within a 100 kpc aperture which varies from $10^{11.2} M_{\odot}$ 
          to $10^{11.7} M_{\odot}$. 
          At fixed "inner" mass ($M_{\star,10}$), massive galaxies display significant
          diversity in their outer profiles. 
          Red boxes indicate galaxies in halos more massive than 
          $\sim 10^{14.0} M_{\odot}$. 
          }
      \label{fig:m100_m10_color}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    Massive galaxies are unique laboratories for studying both cosmology and galaxy 
    formation. 
    Simulations of structure formation within the context of the $\Lambda$-CDM 
    cosmological model make predictions for the hierarchical growth of dark matter halos 
    and galaxies (e.g. \citealt{Baugh1996, DeLucia2006}), but there are many open 
    questions regarding the star-formation history, mass assembly process, and 
    structural evolution of massive galaxies. 
    Massive galaxies are thought to grow according to a ``two-phase'' formation scenario 
    (e.g. \citealt{Oser2010, Oser2012}). 
    In this scenario, the progenitors of $z\sim 0$ massive early-type galaxies (ETGs) 
    undergo a rapid growth phase at $z\sim 2$ triggered either by disk instabilities 
    or gas rich mergers (e.g\citealt{Hopkins2008, Dekel2009}). 
    Observationally, the progenitors of ETGs are thought to correspond to the so-called 
    ``red nuggets'' (e.g. \citealt{Damjanov2009}) which have smaller effective radii 
    ($R_{\mathrm{e}}$; \citealt{Trujillo2006, vanDokkum2008, Cimatti2008}), 
    slightly higher central velocity dispersion and stellar mass density 
    (\mden{}; e.g. \citealt{vandeSande2011, Belli2014}), more disk-like morphologies 
    (e.g. \citealt{vanderWel2011}) than their local descendants 
    (e.g. \citealt{Bezanson2009, vanDokkum2010}).

    Following an initial epoch of early formation, feedback from stars and/or AGN 
    (e.g. \citealt{Sijacki2007, Fabian2012}) efficiently quench star formation in 
    massive galaxies and a large fraction of these massive progenitors become quiescent 
    at $z>1$ (e.g. \citealt{Bezanson2009, Kriek2016}). 
    The second phase in the ``two-phase'' formation scenario is driven by 
    non-dissipative processes such as dry mergers with other galaxies 
    (e.g. \citealt{Naab2006, Khochfar2006}). 
    According to the ``two-phase'' scenario, minor mergers drive the growth of massive 
    galaxies at late times and can help explain the significant increase
    of $R_{\mathrm{e}}$ (e.g. \citealt{Newman2012, vdWel2014}) as well as the build-up 
    of the outer stellar halos of ETGs (e.g.  \citealt{Szomoru2012, Patel2013}).

    According to this two-phase formation scenario, the late time growth of massive ETGs 
    is intrinsically tied to the growth of their host dark matter halos 
    (e.g. \citealt{Leauthaud2012, Behroozi2013, Shankar2013}). 
    Massive ETGs that live at the center of more massive halos should experience 
    a different mass assembly history and should be subject to a larger merger rate 
    compared to ETGs that live in smaller dark matter halos. 
    A natural prediction of the two-phase formation scenario is therefore that the 
    structural properties of massive galaxies should depend on their ``environment''
    \footnote{There are different observational definitions of "environment". 
    In this paper, we use the term ``environment'' and halo mass interchangeably}.

    Previous work has shown that the half-light radii of massive ETGs is tightly 
    correlated with \mstar{} (e.g. \citealt{Shen2003, Guo2009}). 
    Models based on the ``two-phase'' formation scenario naturally predict that this 
    mass--size relation should exhibit an environmental dependence: the effective radii 
    of massive ETGs in more massive halos should be larger than those in less massive
    halos at fixed \mstar{} (e.g. \citealt{Shankar2013, Shankar2014}).

    However, while hints of an environmental dependence in the mass-size relation have 
    been spotted at high-$z$ (e.g. \citealt{Papovich2012, Lani2013, Delaye2014}; but 
    also see \citealt{Rettura2010}), there is no solid evidence for this effect at 
    low-$z$ (e.g. \citealt{Nair2010, HCompany13}; but also see \citealt{Yoon2017}). 
    The absence of an environmental dependence in the mass-size relation is an 
    outstanding challenge to the two-phase formation scenario of ETGs.

    From an observational perspective, we hypothesize that the lack of a detection of 
    this effect may be related a combination of the methodologies employed, as well as 
    the lack of deep high-quality imaging for large numbers of massive ETGs. 
    In particular, massive ETGs have very steep inner stellar density profiles, 
    extremely extended stellar envelopes, and radial-dependent isophotal shapes which 
    make accurate measurements of \mstar{} and $R_{\mathrm{e}}$ very challenging
    (e.g. \citealt{Bernardi2013, DSouza2014}), 
    especially in the presence of shallow imaging data such as the Sloan Digital Sky 
    Survey (SDSS; e.g. \citealt{SDSSDR7, SDSSDR12}).

    In this paper, we take advantage of new high-resolution (median 
    FWHM$\sim 0.6^{\arcsec}$ in $i$-band) and deep ($i$-band surface brightness 
    limit $> 28.5$\sb) imaging from the Hyper-Suprime Cam (HSC) Subaru Strategic 
    Program (SSP; \citealt{HSCDR1; will be referred as the HSC survey} to revisit the 
    question of the environmental dependence in the mass-size relation. 
    The goal of this paper is to compare the \mden{} profiles and structural scaling 
    relations of massive central galaxies in both low and high mass dark matter halos. 
    Fig~\ref{fig:sdss_compare} displays a comparison of the imaging quality of massive 
    ETGs using SDSS versus using the new HSC data. 
    The deep imaging depth and excellent seeing conditions of HSC images make them 
    perfect for mapping the \mstar{} distributions of massive galaxies out to very 
    large radii. 
    With the help of the \redm{} cluster catalog (e.g.\ \citealt{Rykoff2014}; 
    \citealt{Rozo2015b}; please see Section~\ref{ssec:redmapper} for details), we 
    select a large sample ($\sim 15000$) of massive central 
    galaxies with $0.3 < z < 0.5$ using $\sim 100$ square degree of data from the 
    HSC wide layer.

    Motivated by the ``two-phase'' scenario, and also due to the difficulty in 
    providing appropriate model to describe the \mstar{} distribution of massive 
    galaxy from its center to the very outskirt, we focus on \mstar{} within two 
    different physical apertures in this work:

    \begin{itemize}

        \item The stellar mass within 10 kpc (hereafter noted \minn{}). 
            According to the two-phase scenario, the ``in-situ'' star-formation quickly 
            builds up the inner, dense core of massive ETGs.  
            Based on recent observations and simulations (e.g.~\citealt{vanDokkum2010}; 
            \citealt{RodriguezGomez2016}), the in-situ component of massive ETGs is 
            mostly contained within one effective radius ($R_{\mathrm{e}}$, or 5-10 kpc). 
            We use \minn{} as a proxy for the mass forged during the ``in-situ''
            phase. 
            Given the quality of the HSC data, we can reliably measure \minn{} over our 
            redshift range ($1.0^{\arcsec}$ in radius equals 4.4 and 6.1 kpc at redshift
            0.3 and 0.5).

        \item The stellar mass within 100 kpc (hereafter noted \mtot{}). 
            For our galaxy sample, a 100 kpc aperture corresponds to 5-10 
            $\times R_{\mathrm{e}}$. 
            We show in section \ref{ssec:mtotal} that most of the mass for these ETGs 
            can be captured by a 100 kpc radius and that \mtot{} is a good proxy for the 
            ``total'' \mstar{}. 
            Although not perfect, we argue that our measurements of \mtot{} (which are 
            actually measuring the light directly out to 100 kpc) are a better tracer 
            of total \mstar{} than model-dependent results from shallower data 
            (such as SDSS) which rely on extrapolating the light profiles of galaxies 
            out to large radii.

       \end{itemize}
%% ------------------------------------------------------------------------------------ %%

    Massive central galaxies in this work show an intriguing diversity on the plane 
    defined by these two metrics.  
    We preview this using Fig~\ref{fig:m100_m10_color}, which shows a subsample of 
    massive galaxies at $z\sim 0.4$ that share very similar value of \minn{}, but 
    exhibit a large diversity in their outer profiles. 
    Assuming that galaxies at fixed \minn{} share a similar in-situ formation history, 
    it is of great interest to investigate the relation between their present day halo 
    mass and the extend of their outer envelopes. 
    We note that although a circular aperture is shown on Fig~\ref{fig:m100_m10_color}, 
    for our mass measurements, we always use elliptical apertures that follow the 
    average isophotal shape. Finally, given our narrow mass and redshift range, we 
    can safely ignore significant mass growth and structural evolution in this work
    (no star formation, lower merger rate \etal~e.g.\ \citealt{Bellstedt2016},
    \citealt{Inagaki2015}; but also see \citealt{Bai2014}).

    This paper is organized as follows. 
    Section \ref{sec:data} presents our data and our sample selection. 
    Section \ref{sec:ellipse} describes our procedure for extracting 1-D surface 
    brightness profiles. 
    Section \ref{sec:mstar} describes how we estimate stellar mass. 
    Our main results are presented in Section \ref{sec:result} and discussed in 
    Section \ref{sec:discussion}. 
    Section \ref{sec:summary} presents our summary and conclusions.

    Magnitudes use the AB system (\citealt{Oke1983}), and are corrected for Galactic 
    extinction using calibrations from \citet{Schlafly11}.
    In this work, we assume $H_0$ = 70~km~s$^{-1}$ Mpc$^{-1}$, ${\Omega}_{\rm m}=0.3$, 
    and ${\Omega}_{\rm \Lambda}=0.7$.
    Stellar mass is noted \mstar{} and has been derived using a Chabrier Initial Mass 
    Function (IMF; \citealt{Chabrier2003}).     
    $M_{\mathrm{halo}}$ denotes halo mass in general whereas $M_{\rm 200b}$ is 
    explicitly defined as $M_{\rm 200b}\equiv M(<r_{\rm 200b})=200\bar{\rho} 
    \frac{4}{3}\pi r_{\rm 200b}^3$ where $r_{\rm 200b}$
    is the radius at which the mean interior density is equal to 200 times
    the mean matter density ($\bar{\rho}$).

@@

    The Subaru Strategic Program (SSP, \citealt{MiyazakiInPrep}) makes use of the new 
    prime-focus camera, the Hyper Suprime-Cam (HSC;~\citealt{Miyazaki2012}), on the 
    8.2-m Subaru telescope at Mauna Kea. 
    The ambitious multi-layer HSC survey takes advantage of the large field of 
    view (FoV;~1.5 deg in diameter) of this camera and will cover $\sim 1400$ deg$^2$ 
    in 5 broad bands ($grizY$) to a limiting depth of $r \sim 26$ mag 
    in the \texttt{WIDE} layer. 
    This work is based on the internal data release \texttt{S15B}, which covers 
    $\sim 100$ deg$^2$ in all 5-band to full \texttt{WIDE} depth.  
    The regions covered by this release overlap with a number of spectroscopic surveys 
    (e.g.\ SDSS/BOSS: \citealt{Eisenstein2011}, \citealt{Alam2015}; 
    GAMA: \citealt{Driver2011}, \citealt{Liske2015}).

@@

    For each galaxy, \texttt{hscPipe} measures a \cmodel{} magnitude using an approach 
    that is similar to SDSS (\citealt{BoschInPrep}). 
    However, as opposed to SDSS, the HSC \cmodel{} is based on forced photometry which 
    means that it can accurately measure both the \textit{fluxes and colors of galaxies}. 
    The HSC \cmodel{} algorithm fits the flux distribution of each object using a 
    combination of a de~Vaucouleur and an exponential component and accounts for the PSF. 
    The performance of this algorithm has been tested using synthetic objects 
    (\citealt{SynPipeInPrep}), and the results indicate that, generally speaking, 
    the HSC \cmodel{} photometry is accurate down to $i >25.0$ mag.  
    However, \cmodel{} currently systematically underestimates the total fluxes of 
    massive ETGs with extended stellar distributions. 
    This is caused by an intrinsic limitation of \cmodel{} as it is incapable of
    modeling profiles with extremely extended outskirts, a problem that is exacerbated 
    at the depth of the HSC survey. 
    In addition, at the depth of the HSC survey, accurate deblending in the vicinity of
    large ETGs where satellites and background galaxies often blend with the low surface 
    brightness stellar envelope is a challenging problem. 
    The deblending method implemented by the \texttt{hscPipe} currently tends to 
    ``over-deblend'' the outskirts of bright galaxies and leads to an 
    under-estimation of the the total flux of massive ETGs (this is discussed further in 
    \citealt{BoschInPrep}).  
    For these reasons, our results will be based on custom developed code to measure 
    the luminosities and stellar masses of massive galaxies. 
    We use the HSC \texttt{hscPipe} photometry for two purposes: 
    1) to perform a first broad sample selection, and 2) to estimate the average 
    color of massive galaxies.

@@

    We begin by using a broad luminosity cut to select an initial sample of massive 
    galaxies at $z < 0.5$ from the HSC photometric catalog. 
    Based on \citep{Leauthaud2016}, galaxies with \logms{}$\geq 11.5$ mostly have 
    $i_{\mathrm{SDSS, cModel}} \leq 21.0$ mag. 
    We therefore select our initial sample to be brighter than 
    $i_{\mathrm{HSC, cModel}} \leq 21.5$\footnote{We neglect small differences between 
    the response curves of SDSS-$i$ and HSC-$i$ filters.} 
    and also limit our sample to regions that have reached the required depth of 
    the \texttt{WIDE} survey in the $i$-band.
    %% The SQL search is saved as "sample.sql" 
    %% The master catalog used here is "dr1_wide_galaxy_icmodel_21.5.fits"
    %%   The original catalogs contain 2275477 objects

    We further select extended objects with no deblending errors, with well defined 
    centroids, and with \texttt{cModel} magnitudes in all five bands. 
    After removing objects that have pixels affected by saturation, cosmic-rays, or 
    other optical artifacts\footnote{each criterion removes less than 8\% of the 
    entire sample.}.This sample corresponds to 1760845 galaxies and will be referred 
    as \texttt{hscPho}. 
    %% Saved as "dr1_wide_galaxy_hscPho.fits"
